\input{header}
\title{
  Effective Resistances is a Hypermetric
}
\author{Timothy Chu\\
  Carnegie Mellon \\
    \texttt{tzchu@andrew.cmu.edu}
}
\date{\today}
\begin{document}

\maketitle
\thispagestyle{empty}

\begin{abstract} The effective resistance is a widely used metric.
It is known to be of negative type.

Negative type metrics are known to contain a wide class of metrics. In
particular, it is known that L2 is contained inside L1, which is
contained inside the space of Hypermetrics. The space of Hypermetrics is
in turn contained inside the space of negative type metrics.

We aim to precisely determine how effective resistance metrics fit into
this heirarchy of metrics: which metric spaces contain all effective
resistance metrics, and which metrics are contained inside the space of
effective resistance metrics?

In this paper, we show that L2 is not contained in the effective
resistance metrics, and that the effective resistance metrics are
contained in the hypermetrics.
To do this, we introduce both an easily computable criterion for
determining whether a given distance can be induced by an effective
resistance distance, and a generalization of the Rayleigh
Monotonicity law. These two may be of independent interest when
studying properties of Effective Resistances.

\end{abstract}
\input{introduction}
\section{Overview}
\section{A Quadratic Time Criterion for Effective Resistance.}
\section{A Generalization of Rayleigh's Monotonicity}
\section{Effective Resistance Obeys the Hypermetric Inequalities.}
\section{Open Problems}
Hello.
\end{document}
